Climate variability indices for ecological and crop models in R: the `climatrends` package

### 2020-05-24 inst/paper/paper.Rmd
beans_data

```{r get data, include=FALSE}
library("knitr")
library("kableExtra")
library("magrittr")
funtbl <- read.csv("available_functions.csv")
```

@@

>>>>

```{r get data, include=FALSE}
library("knitr")
library("kableExtra")
library("tidyverse")
library("climatrends")
library("PlackettLuce")
funtbl <- read.csv("available_functions.csv")
load("inst/paper/cbean.rda")
```

@@

```{r }
```
